### 2021-11-21 paper/output/document/application.tex
early applications work

%
\begin{isabellebody}%
\setisabellecontext{application}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{sec:applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will demonstrate possible applications of my formalization of the FUL. I 
will present two kinds of applications. First, I will formalize a classical ethical dilemma in 
Kantian literature, the case of the murderer at the door. This will demonstrate the utility of computational
ethics in helping philosophers think about ethical dilemmas. Second, I will encode some ``common sense"
facts into the system and then test the results of applying this more powerful system to common
ethical dilemmas. This section will serve as a prototype of the kind of reasoning that this kind of 
computational ethics can do and will demonstrate the utility of computational ethics in performing 
everyday ethical reasoning. This section will also outline what future work is necessary to use an 
ethical reasoner like the one I build in practice. Finally, I will also philosophically analyze the possibility and value of 
applications like these. Specifically, I will consider to what extent humans should let computers do 
ethical reasoning on our behalf.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Right to Lie \label{sec:rtl}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I draw on examples of ethical reasoning as presented in Korsgaard's right to lie.
She analyzes the example of someone who shows up at your door and asks, "Is Sara home?" Unbeknownst to them, 
you know that they want to know Sara's location in order to murder her. Ordinary moral intuition seems
to imply that in this situation, if Sara is home, you should lie and say that she is not in order to 
protect her from the murderer. However, the categorical imperative seems to prohibit lying in all 
circumstances. More specifically, when universalized, lies will no longer be believed, so it seems 
like lying could never be an effective way of achieving any goal when universalized. Korsgaard points out
that ``we believe what is said to us in a given context because most of the time people in that context 
say what they really think" \citep[4]{KorsgaardRTL}. First, I will formalize this argument.

@@

This section will provide additional examples of the kinds of commons sense required to get my system
off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
to achieve results as robust and powerful as possible. This serves as evidence for the ease of automating
Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
that I make.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/application.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%55=20%:%
%:%67=22%:%
%:%68=23%:%
%:%69=24%:%
%:%70=25%:%
%:%71=26%:%
%:%72=27%:%
%:%73=28%:%
%:%74=29%:%
%:%75=30%:%
%:%76=31%:%
%:%77=32%:%
%:%79=34%:%
%:%80=34%:%
%:%82=35%:%
%:%83=35%:%
%:%84=36%:%
%:%85=36%:%
%:%87=37%:%
%:%88=37%:%
%:%89=38%:%
%:%90=38%:%
%:%91=39%:%
%:%92=40%:%
%:%93=40%:%
%:%94=41%:%
%:%96=42%:%
%:%97=42%:%
%:%98=47%:%
%:%99=48%:%
%:%100=48%:%
%:%101=49%:%
%:%103=50%:%
%:%104=51%:%
%:%105=52%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%117=61%:%
%:%118=62%:%
%:%120=64%:%
%:%121=64%:%
%:%123=65%:%
%:%124=65%:%
%:%125=66%:%
%:%126=66%:%
%:%128=67%:%
%:%129=68%:%
%:%132=70%:%
%:%134=72%:%
%:%135=72%:%
%:%136=73%:%
%:%137=74%:%
%:%138=75%:%
%:%139=76%:%
%:%140=77%:%
%:%142=78%:%
%:%143=78%:%
%:%144=79%:%
%:%146=80%:%
%:%147=81%:%
%:%148=81%:%
%:%149=82%:%
%:%151=83%:%
%:%152=83%:%
%:%153=84%:%
%:%155=85%:%
%:%156=86%:%
%:%157=86%:%
%:%158=87%:%
%:%165=88%:%
%:%166=88%:%
%:%167=89%:%
%:%168=89%:%
%:%169=90%:%
%:%170=90%:%
%:%172=91%:%
%:%173=92%:%
%:%174=93%:%
%:%175=94%:%
%:%176=94%:%
%:%177=95%:%
%:%178=95%:%
%:%179=96%:%
%:%180=96%:%
%:%181=97%:%
%:%182=97%:%
%:%183=98%:%
%:%184=98%:%
%:%185=98%:%
%:%186=99%:%
%:%196=101%:%
%:%197=102%:%
%:%198=103%:%
%:%199=104%:%
%:%200=105%:%
%:%201=106%:%
%:%202=107%:%
%:%203=108%:%
%:%204=109%:%
%:%205=110%:%
%:%206=111%:%
%:%207=112%:%
%:%208=113%:%
%:%209=114%:%
%:%210=115%:%
%:%211=116%:%
%:%212=117%:%
%:%213=118%:%
%:%214=119%:%
%:%215=120%:%
%:%216=121%:%
%:%217=122%:%
%:%218=123%:%
%:%219=124%:%
%:%220=125%:%
%:%221=126%:%
%:%222=127%:%
%:%223=128%:%
%:%224=129%:%
%:%225=130%:%
%:%226=131%:%
%:%227=132%:%
%:%228=133%:%
%:%229=134%:%
%:%230=135%:%
%:%231=136%:%
%:%232=137%:%
%:%233=138%:%
%:%234=139%:%
%:%235=140%:%
%:%236=141%:%
%:%237=142%:%
%:%238=143%:%
%:%239=144%:%
%:%240=145%:%
%:%241=146%:%
%:%242=147%:%
%:%243=148%:%
%:%244=149%:%
%:%245=150%:%
%:%246=151%:%
%:%247=152%:%
%:%248=153%:%
%:%249=154%:%
%:%250=155%:%
%:%251=156%:%
%:%252=157%:%
%:%253=158%:%
%:%254=159%:%
%:%255=160%:%
%:%256=161%:%
%:%257=162%:%
%:%258=163%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{application}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{sec:applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will demonstrate possible applications of my formalization of the FUL. I 
will present two kinds of applications. First, I will formalize a classical ethical dilemma in 
Kantian literature, the case of the murderer at the door. This will demonstrate the utility of computational
ethics in helping philosophers think about ethical dilemmas. Second, I will encode some ``common sense"
facts into the system and then test the results of applying this more powerful system to common
ethical dilemmas. This section will serve as a prototype of the kind of reasoning that this kind of 
computational ethics can do and will demonstrate the utility of computational ethics in performing 
everyday ethical reasoning. This section will also outline what future work is necessary to use an 
ethical reasoner like the one I build in practice. Finally, I will also philosophically analyze the possibility and value of 
applications like these. Specifically, I will consider to what extent humans should let computers do 
ethical reasoning on our behalf.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Preliminary Lying Work \label{sec:lyingprelim}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I draw on examples of ethical reasoning as presented in Korsgaard's right to lie.
She analyzes the example of someone who shows up at your door and asks, "Is Sara home?" Unbeknownst to them, 
you know that they want to know Sara's location in order to murder her. Ordinary moral intuition seems
to imply that in this situation, if Sara is home, you should lie and say that she is not in order to 
protect her from the murderer. However, the categorical imperative seems to prohibit lying in all 
circumstances. More specifically, when universalized, lies will no longer be believed, so it seems 
like lying could never be an effective way of achieving any goal when universalized. Korsgaard points out
that ``we believe what is said to us in a given context because most of the time people in that context 
say what they really think" \citep[4]{KorsgaardRTL}. First, I will formalize this argument.

@@

This section will provide additional examples of the kinds of commons sense required to get my system
off the ground. I will aim to use as lean and uncontroversial of a common sense database as possible
to achieve results as robust and powerful as possible. This serves as evidence for the ease of automating
Kantian ethics, an example of what additional work my system requires, and a demonstration of the contributions
that I make.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Now that I have formalized Korsgaard's sketch of an argument for why lying is prohibited, I will 
implement her argument for why jokes are permissible. Specifically, she considers a joke a story that is 
false and argues that joking is permissible because ``the universal practice of lying in the context of jokes
does not interfere with the purpose of jokes, which is to amuse and does not depend on
deception" \citep[4]{KorsgaardRTL}. Let's define a joke.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ joke{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}maxim{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}joke\ {\isasymequiv}\ {\isasymlambda}\ {\isacharparenleft}c{\isacharcomma}\ a{\isacharcomma}\ g{\isacharparenright}{\isachardot}\ \ {\isasymexists}t{\isachardot}\ {\isacharparenleft}a\ \isactrlbold {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ t{\isacharparenright}{\isacharparenright}\ {\isasymand}\ {\isasymnot}\ {\isacharparenleft}{\isasymexists}p{\isachardot}\ {\isasymforall}w{\isachardot}\ {\isacharparenleft}g\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ p\ t{\isacharparenright}{\isacharparenright}\ w{\isacharparenright}{\isachardoublequoteclose}%
\begin{isamarkuptext}%
This definition of a joke merely defines a joke as a falsehood uttered for some purpose that 
emph{doesn't} require deception, where deception involves someone believing the uttered falsehood. Notice 
that this is quite a thin definition of a joke; it doesn't require any conception of humor but merely
distinguishes jokes from lies. As far as common sense reasoning goes, this is a relatively thin proposition. 
I will now demonstrate that this conception of a joke is sufficient to show that joking is permissible.

I will reuse some of the logical structure from the lying example, namely the maxim $m$ and subject $me$. 
I will also reuse the same assumptions to show that, under the same set of ``common sense" facts, lying is
prohibited but joking is not.%
\ joking{\isacharunderscore}not{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}joke\ m{\isachardoublequoteclose}\isanewline
\isamarkupcmt{$m$ is a maxim about joking. Precisely, it is a maxim in which the action is to knowingly utter a 
falsehood and the goal does not require that someone believe this falsehood.%
\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. Recall that this
is the most significant piece of common sense reasoning necessary for this example.%
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}permissible\ m\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ %
\isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}smt\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{3}}{\isacharparenright}\ case{\isacharunderscore}prod{\isacharunderscore}conv{\isacharparenright}%
To summarize, in this section I introduce the role of common sense reasoning in my system and 
demonstrate the kind of common sense facts necessary to show that lying is generally prohibited and 
jokes are permissible. I conclude that this kind of sophisticated ethical reasoning requires relatively
thin common sense facts and robust definitions of the terms involved. Thus, while common sense reasoning 
is an obstacle that must be overcome for my system to be used, it is not insurmountable.%
\isadelimdocument
\endisadelimdocument
\isatagdocument
\isamarkupsubsection{Lying to a Liar \label{sec:lyingtoliar}%
}
\isamarkuptrue%
\endisatagdocument
{\isafolddocument}%
\isadelimdocument
\endisadelimdocument
Once Korsgaard does some preliminary work differentiating between lies and jokes, she begins the 
meat of her argument, which examines the case of the murderer at the door. Recall that the murderer
appears at your door and asks if their intended victim is at home. Ordinary intuition requires that it 
is at the very least permissible (if not obligatory) to lie to the murderer in order to protect the 
victim. Korsgaard notes that a murderer who wishes to find their victim cannot simply announce their
intentions to murder; instead, he must ``must suppose that you do not know who he is and
what he has in mind" \citep[5]{KorsgaaardRTL}. Thus, she can modify the maxim in question and specifies
that when someone lies to you, you are allowed to lie to them. The maxim of lying to the murderer is 
thus actually the maxim of lying to a liar, which she argues is permissible. In this section, I will 
formalize her argument for lying to a liar.%
\ murderer{\isacharcolon}{\isacharcolon}s\isanewline
\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcolon}{\isacharcolon}t\isanewline
\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcolon}{\isacharcolon}t\isanewline
\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\isanewline
\ find{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
\ protect{\isacharunderscore}victim{\isacharcolon}{\isacharcolon}t\isanewline
\ murderers{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}murderers{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door{\isacharcomma}\ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharcomma}\ find{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcolon}{\isacharcolon}t\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}murderer{\isacharunderscore}at{\isacharunderscore}door\ {\isasymequiv}\ W\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
\ my{\isacharunderscore}maxim{\isacharcolon}{\isacharcolon}maxim\ \isakeyword{where}\ \isanewline
{\isachardoublequoteopen}my{\isacharunderscore}maxim\ {\isasymequiv}\ {\isacharparenleft}murderer{\isacharunderscore}at{\isacharunderscore}door{\isacharcomma}\ \ {\isasymlambda}s{\isachardot}\ knowingly{\isacharunderscore}utter{\isacharunderscore}falsehood\ s\ victim{\isacharunderscore}not{\isacharunderscore}home{\isacharcomma}\ protect{\isacharunderscore}victim{\isacharparenright}{\isachardoublequoteclose}%
First, I will show that using the same common sense reasoning justified above, the murderer's
maxim is prohibited.%
\ murderers{\isacharunderscore}maxim{\isacharunderscore}prohibited{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer\ w{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Initial set-up, the murderer's maxim is a well-formed maxim composed of some circumstances, act, and goal.%
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}believe\ me\ not{\isacharunderscore}a{\isacharunderscore}murderer{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Assumption that if everyone utters false statement t, then no one will believe t. Recall that this
is the most significant piece of common sense reasoning necessary for this example.%
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymforall}w{\isachardot}\ when{\isacharunderscore}at{\isacharunderscore}my{\isacharunderscore}door\ w{\isachardoublequoteclose}\isanewline
\isamarkupcmt{Restrict our focus to worlds in which the circumstance of the murderer being at my door holds, as 
these are the morally interesting worlds for this example. Basically an irrelevant technical detail.%
\ \ \isakeyword{shows}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}prohibited\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\ \ \ \isanewline
\isamarkupcmt{Again, this proof is too heavy for Isabelle to finish on its own, so I needed to specify some
intermediate steps. The same intermediate steps as above sufficed.%
\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}p\ w{\isachardot}\ {\isacharparenleft}W\ murderers{\isacharunderscore}maxim\ p{\isacharparenright}\ w{\isacharparenright}\ {\isasymlongrightarrow}\ {\isacharparenleft}{\isasymTurnstile}\ {\isacharparenleft}find{\isacharunderscore}victim\ \isactrlbold {\isasymrightarrow}\ {\isacharparenleft}\isactrlbold {\isasymnot}\ find{\isacharunderscore}victim{\isacharparenright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
\ \ \ \isacommand{have}\isamarkupfalse%
\ {\isachardoublequoteopen}not{\isacharunderscore}universalizable\ murderers{\isacharunderscore}maxim\ murderer{\isachardoublequoteclose}\isanewline
\ \ \ \ \ \isacommand{using}\isamarkupfalse%
\ assms{\isacharparenleft}{\isadigit{2}}{\isacharparenright}\ assms{\isacharparenleft}{\isadigit{4}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline
\ \ \ \isacommand{thus}\isamarkupfalse%
\ \ \ \ \ \isacommand{using}\isamarkupfalse%
\ FUL\ assms{\isacharparenleft}{\isadigit{1}}{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ blast\isanewline
\ \isacommand{qed}\isamarkupfalse%
\ lying{\isacharunderscore}to{\isacharunderscore}liar{\isacharunderscore}permissible{\isacharcolon}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ murderers{\isacharunderscore}maxim\ murderer{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{assumes}\ {\isachardoublequoteopen}{\isasymTurnstile}\ {\isacharparenleft}well{\isacharunderscore}formed\ my{\isacharunderscore}maxim\ me{\isacharparenright}{\isachardoublequoteclose}\isanewline
\ \ \isakeyword{shows}\ True%
\ %
\isacommand{oops}\isamarkupfalse%
let M be the murderer and me be you.
when M lies to you, you can lie to M.

when M knowingly utters a falsehood with the goal of you believing the falsehood, you can lie to M.

when M knowingly utters falsehood T with the goal of you believing T, you can knowingly
utter falsehood K with the goal of M believing K.

let circumstances C = when M knowingly utters falsehood T with the goal of you believing T
let A = knowingly utter falsehood K with the goal of M believing K
everyone adopts maxim, "C -> A" 
if everyone adopts maxim "C->A", if they believe you believe C, then won't believe A (specifically K) (modify the universal lying assumption)
M doesn't believe you believe C
so M will believe A (might need to add this as an axiom)%
\isadelimdocument
\endisadelimdocument
\isatagdocument
\endisatagdocument
{\isafolddocument}%
\isadelimdocument
\endisadelimdocument
\isadelimtheory
\endisadelimtheory
\isatagtheory
\endisatagtheory
{\isafoldtheory}%
\isadelimtheory
\endisadelimtheory
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/paper/application.thy%:%
%:%24=6%:%
%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%40=12%:%
%:%41=13%:%
%:%42=14%:%
%:%43=15%:%
%:%44=16%:%
%:%45=17%:%
%:%46=18%:%
%:%55=20%:%
%:%67=22%:%
%:%68=23%:%
%:%69=24%:%
%:%70=25%:%
%:%71=26%:%
%:%72=27%:%
%:%73=28%:%
%:%74=29%:%
%:%75=30%:%
%:%76=31%:%
%:%77=32%:%
%:%79=34%:%
%:%80=34%:%
%:%82=35%:%
%:%83=35%:%
%:%84=36%:%
%:%85=36%:%
%:%87=37%:%
%:%88=37%:%
%:%89=38%:%
%:%90=38%:%
%:%91=39%:%
%:%92=40%:%
%:%93=40%:%
%:%94=41%:%
%:%96=42%:%
%:%97=42%:%
%:%98=47%:%
%:%99=48%:%
%:%100=48%:%
%:%101=49%:%
%:%103=50%:%
%:%104=51%:%
%:%105=52%:%
%:%108=54%:%
%:%109=55%:%
%:%110=56%:%
%:%111=57%:%
%:%112=58%:%
%:%113=59%:%
%:%117=61%:%
%:%118=62%:%
%:%120=64%:%
%:%121=64%:%
%:%123=65%:%
%:%124=65%:%
%:%125=66%:%
%:%126=66%:%
%:%128=67%:%
%:%129=68%:%
%:%132=70%:%
%:%134=72%:%
%:%135=72%:%
%:%136=73%:%
%:%137=74%:%
%:%138=75%:%
%:%139=76%:%
%:%140=77%:%
%:%142=78%:%
%:%143=78%:%
%:%144=79%:%
%:%146=80%:%
%:%147=81%:%
%:%148=81%:%
%:%149=82%:%
%:%151=83%:%
%:%152=83%:%
%:%153=84%:%
%:%155=85%:%
%:%156=86%:%
%:%157=86%:%
%:%158=87%:%
%:%165=88%:%
%:%166=88%:%
%:%167=89%:%
%:%168=89%:%
%:%169=90%:%
%:%170=90%:%
%:%172=91%:%
%:%173=92%:%
%:%174=93%:%
%:%175=94%:%
%:%176=94%:%
%:%177=95%:%
%:%178=95%:%
%:%179=96%:%
%:%180=96%:%
%:%181=97%:%
%:%182=97%:%
%:%183=98%:%
%:%184=98%:%
%:%185=98%:%
%:%186=99%:%
%:%196=101%:%
%:%197=102%:%
%:%198=103%:%
%:%199=104%:%
%:%200=105%:%
%:%201=106%:%
%:%202=107%:%
%:%203=108%:%
%:%204=109%:%
%:%205=110%:%
%:%206=111%:%
%:%207=112%:%
%:%208=113%:%
%:%209=114%:%
%:%210=115%:%
%:%211=116%:%
%:%212=117%:%
%:%213=118%:%
%:%214=119%:%
%:%215=120%:%
%:%216=121%:%
%:%217=122%:%
%:%218=123%:%
%:%219=124%:%
%:%220=125%:%
%:%221=126%:%
%:%222=127%:%
%:%223=128%:%
%:%224=129%:%
%:%225=130%:%
%:%226=131%:%
%:%227=132%:%
%:%228=133%:%
%:%229=134%:%
%:%230=135%:%
%:%231=136%:%
%:%232=137%:%
%:%233=138%:%
%:%234=139%:%
%:%235=140%:%
%:%236=141%:%
%:%237=142%:%
%:%238=143%:%
%:%239=144%:%
%:%240=145%:%
%:%241=146%:%
%:%242=147%:%
%:%243=148%:%
%:%244=149%:%
%:%245=150%:%
%:%246=151%:%
%:%247=152%:%
%:%248=153%:%
%:%249=154%:%
%:%250=155%:%
%:%251=156%:%
%:%252=157%:%
%:%253=158%:%
%:%254=159%:%
%:%255=160%:%
%:%256=161%:%
%:%257=162%:%
%:%258=163%:%
%:%262=165%:%
%:%263=166%:%
%:%264=167%:%
%:%265=168%:%
%:%266=169%:%
%:%268=171%:%
%:%269=171%:%
%:%270=172%:%
%:%272=174%:%
%:%273=175%:%
%:%274=176%:%
%:%275=177%:%
%:%276=178%:%
%:%277=179%:%
%:%278=180%:%
%:%279=181%:%
%:%280=182%:%
%:%282=184%:%
%:%283=184%:%
%:%284=185%:%
%:%285=186%:%
%:%286=187%:%
%:%287=188%:%
%:%288=189%:%
%:%290=190%:%
%:%291=190%:%
%:%292=191%:%
%:%294=192%:%
%:%295=193%:%
%:%296=193%:%
%:%297=194%:%
%:%299=195%:%
%:%300=196%:%
%:%301=196%:%
%:%302=197%:%
%:%304=198%:%
%:%305=199%:%
%:%306=199%:%
%:%307=200%:%
%:%310=201%:%
%:%314=201%:%
%:%315=201%:%
%:%324=203%:%
%:%325=204%:%
%:%326=205%:%
%:%327=206%:%
%:%328=207%:%
%:%337=209%:%
%:%349=211%:%
%:%350=212%:%
%:%351=213%:%
%:%352=214%:%
%:%353=215%:%
%:%354=216%:%
%:%355=217%:%
%:%356=218%:%
%:%357=219%:%
%:%358=220%:%
%:%360=222%:%
%:%361=222%:%
%:%362=223%:%
%:%363=223%:%
%:%364=224%:%
%:%365=224%:%
%:%366=225%:%
%:%367=225%:%
%:%368=226%:%
%:%369=226%:%
%:%370=227%:%
%:%371=227%:%
%:%372=228%:%
%:%373=228%:%
%:%374=229%:%
%:%375=230%:%
%:%376=230%:%
%:%377=231%:%
%:%378=232%:%
%:%379=232%:%
%:%380=233%:%
%:%382=235%:%
%:%383=236%:%
%:%385=238%:%
%:%386=238%:%
%:%387=239%:%
%:%389=240%:%
%:%390=240%:%
%:%391=241%:%
%:%392=242%:%
%:%394=243%:%
%:%395=244%:%
%:%396=244%:%
%:%397=245%:%
%:%399=246%:%
%:%400=247%:%
%:%401=247%:%
%:%402=248%:%
%:%409=249%:%
%:%410=249%:%
%:%412=250%:%
%:%413=251%:%
%:%414=251%:%
%:%415=252%:%
%:%416=252%:%
%:%417=253%:%
%:%418=253%:%
%:%419=253%:%
%:%420=254%:%
%:%421=254%:%
%:%422=255%:%
%:%423=255%:%
%:%424=255%:%
%:%425=256%:%
%:%426=256%:%
%:%427=257%:%
%:%428=257%:%
%:%429=257%:%
%:%430=258%:%
%:%436=258%:%
%:%439=259%:%
%:%440=260%:%
%:%441=261%:%
%:%442=261%:%
%:%443=262%:%
%:%444=263%:%
%:%445=264%:%
%:%447=264%:%
%:%451=264%:%
%:%461=267%:%
%:%462=268%:%
%:%463=269%:%
%:%464=270%:%
%:%465=271%:%
%:%466=272%:%
%:%467=273%:%
%:%468=274%:%
%:%469=275%:%
%:%470=276%:%
%:%471=277%:%
%:%472=278%:%
%:%473=279%:%
%:%474=280%:%
